### 2014-10-24 PrivacyProtection-2014-09-09.tex
Added Privacy Policy Section
Revised Threats.

\subsubsection{Threats}
This section outlines the potential threats (Figure \ref{figure:Live+Gov Threats}) for Citizen privacy in the proposed monitoring and mining System.
We derive threats from known conflicts of interests \ref{subsubsection:Conflicts of Interests} and vulnerabilities \ref{subsubsection:Vulnerabilities}

@@

0. Bad Architecture
-------------------
Description: The Service Provider does not offer tools for the citizen to control his data.
COI:            Privacy vs. System Complexity
Vulneratbility: Bad system design
Asset:          Control over Data

1. Surveillance
---------------
Description:   External infiltrates infrastructure in order to spy on citizen
COI:           Privacy vs. External Power
Vulnerability: Insecure Infrastructure, Insecure Communication
Asset:         Data transferred and stored in data center.

@@

COI:         Privacy vs. Financial Profit
             Reputation of Service Provider vs. Political Activism
             Reputation of Local Authority vs. Political Activism
Vuln.:       Insecure Infrastructure, Insecure Communication
Asset:       Data transmitted or stored in data center.

3. Information Leak
-------------------
Description: Like an external person in Scenario (2) an employee of the service provider has selfish interests to gain money, make political statements or harm his employer.
In order to pursue this interest he can steal personal data and sell it or release it to the public.

COI:         Privacy vs. Financial Profit
             Reputation of Service Provider vs. Political Activism
             Reputation of Local Authority vs. Political Activism
Vuln.:       Unhappy Employee, Lax Access Rules.
Asset:       Data stored in data center.

4. Social Engineering
---------------------
Description: An External can manipulate Local Authorities or Service Providers to give them personal information that he can then sell or disclose.

COI:         Privacy vs. Financial Profit
             Reputation of Service Provider vs. Political Activism
             Reputation of Local Authority vs. Political Activism
Vuln.:       Unhappy Employee, Lax Access Rules.
Asset:       Data stored in data center.

@@

%\includegraphics{../diagrams/png/sensor-privacy-matrix.png}
\input{./figures/LG-Sensor-Privacy-Matrix}
%\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}

>>>>

\subsubsection{Threats}
This section outlines the potential threats (Figure \ref{figure:Live+Gov Threats}) for Citizen privacy in the proposed monitoring and mining System.

We derive threats from known conflicts of interests \ref{subsubsection:Conflicts of Interests} and vulnerabilities \ref{subsubsection:Vulnerabilities}

Abstract Description of Threats.

@@

Loss Calibration:
* High:   Leak of information to Peers, e.g. spouse gets GPS data and finds out cheating.
          Subjects is added to No-Fly list due to Government spying.
          Public leak of private information;
* Medium: Undisclosed processing of personal data;
          Potentially disclosure to third parties that are unrelated to subjct.
* Low:    Loss of control over data.
* None: -

0. Bad Architecture
-------------------
Description:    The Service Provider does not offer tools for the citizen to control his data.
COI:            Privacy vs. System Complexity
Vulneratbility: Bad system design
Asset:          All collected data

Likeliness: Always
Loss: Low (Control is lost, no direct harm done)
Risk:      5

1. Excessive Data Mining
------------------------
Description: The Service Provider and/or the Local Authority extract more private information from the collected data, than the citizen agreed to.
E.g. the Service Provider wants to test a new product, and uses old data collected for a different purpose.
E.g. the Local Authority wants to analyze collected data from fare evasions.

COI: Privacy vs. Buisness Intelligence of Local Authority, Privacy vs. Financial Profit of Serivce Provider.
Vuln.: Lax data handling policies; Unaware citizen; Weak law enforcement
Affected Data: Potential Information extracted from raw data.

Likeliness: High
Loss:      Medium (Control is lost, no direct harm done)
Risk:      5

@@

COI:         Privacy vs. Financial Profit
             Reputation of Service Provider vs. Political Activism
             Reputation of Local Authority vs. Political Activism
Vuln.:       Insecure Infrastructure, Insecure Communication
Affected Data:  Data transmitted or stored in data center: GPS trips, HAR-records.

Likeliness: Low-Medium
Loss: High
Risk: 4-5

3. Surveillance
---------------
Description:   External infiltrates infrastructure in order to spy on citizen
COI:           Privacy vs. External Power
Vulnerability: Insecure Infrastructure, Insecure Communication
Affected Data:         Data transferred and stored in data center.

Likeliness: Medium (Government*), Low (Third parties)
Loss: High (Control is lost, potential harm by due to Government action)
Risk:      6/4

* Government, has also other tools at it's disposal

4. Information Leak
-------------------
Description: Like an external person in Scenario (2) an employee of the service provider has selfish interests to gain money, make political statements or harm his employer.
In order to pursue this interest he can steal personal data and sell it or release it to the public.

COI:         Privacy vs. Financial Profit
             Reputation of Service Provider vs. Political Activism
             Reputation of Local Authority vs. Political Activism
Vuln.:       Unhappy Employee, Lax Access Rules.
Affected Data:       Data stored in data center.

Likeliness: Low
Loss: High (public leak)
Risk: 4

5. Social Engineering
---------------------
Description: An External can manipulate Local Authorities or Service Providers to give them personal information that he can then sell or disclose.

COI:         Privacy vs. Financial Profit
             Reputation of Service Provider vs. Political Activism
             Reputation of Local Authority vs. Political Activism
Vuln.:       Unhappy Employee, Lax Access Rules.
Affected Data:       Data stored in data center.

Likeliness: Low
Loss: High
Risk: 4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\includegraphics{../diagrams/png/sensor-privacy-matrix.png}
%\input{./figures/LG-Sensor-Privacy-Matrix}
\input{./figures/LG-Implicit-Sensor-Privacy-Matrix}
